\pkg{fitdistrplus}: An \proglang{R} Package for Fitting Distributions

### 2013-05-15 JSS/fitdistrplus/paper2JSS.Rnw
take into account pre-screening.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/riskassessment@250 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

The bootstrap method can also be used to calculate confidence intervals on quantiles 
of the fitted distribution.
For this purpose, a generic \code{quantile} function is provided for class \code{bootdist}. 
By default, $95\%$ percentiles bootstrap confidence intervals of quantiles are provided.
Going back to the previous example from ecotoxicolgy, this function can be used to 
estimate the uncertainty associated to the HC5 estimation, for example from the previously fitted
Burr distribution to the \code{endosulfan} data set.
 %%% R code
<<fitATV.lnorm.quantile, echo=TRUE,results=hide>>=
quantile(bendo.B, probs = 0.05)
@
\begin{footnotesize}
<<fitATV.lnorm.quantileb, echo=FALSE>>=
quantile(bendo.B, probs = 0.05)
@
\end{footnotesize}

@@

When fitting discrete distributions, the Chi-squared statistic is computed by 
the \code{gofstat} function using cells defined 
by the argument \code{chisqbreaks} or cells automatically defined from the data in order 
to reach roughly the same number of observations per cell. This number is roughly equal to the argument
\code{meancount}, or sligthly greater if there are some ties. 
The choice to define cells from the empirical distribution (data), and not from the
theoretical distribution, was done to enable the comparison of Chi-squared values obtained
with different distributions fitted on a same data set.
If arguments \code{chisqbreaks} and \code{meancount} 
are both omitted, \code{meancount} is fixed in order to obtain roughly $(4n)^{2/5}$ cells, 
with $n$ the length of the data set \citep{Vose10}. Using this default option the two previous fits are 
compared as follows, 
giving the preference
to the negative binomial distribution, from both Chi-squared statistics and information criteria:
%%% R code
<<fittoxocara.poisnbinom.gof, echo=TRUE, fig=FALSE>>=
gofstat(list(ftoxo.P,ftoxo.nb),fitnames = c("Poisson","negative binomial"))
@

>>>>

The bootstrap method can also be used to calculate confidence intervals on quantiles 
of the fitted distribution.
For this purpose, a generic \code{quantile} function is provided for class \code{bootdist}. 
By default, $95\%$ percentiles bootstrap confidence intervals of quantiles are provided.
Going back to the previous example from ecotoxicolgy, this function can be used to 
estimate the uncertainty associated to the HC5 estimation, for example from the previously fitted
Burr distribution to the \code{endosulfan} data set.
 %%% R code
<<fitATV.lnorm.quantile, echo=TRUE,results=hide>>=
quantile(bendo.B, probs = 0.05)
@
\begin{small}
<<fitATV.lnorm.quantileb, echo=FALSE>>=
quantile(bendo.B, probs = 0.05)
@
\end{small}

@@

When fitting discrete distributions, the Chi-squared statistic is computed by 
the \code{gofstat} function using cells defined 
by the argument \code{chisqbreaks} or cells automatically defined from the data in order 
to reach roughly the same number of observations per cell. This number is roughly equal to the argument
\code{meancount}, or sligthly greater if there are some ties. 
The choice to define cells from the empirical distribution (data), and not from the
theoretical distribution, was done to enable the comparison of Chi-squared values obtained
with different distributions fitted on a same data set.
If arguments \code{chisqbreaks} and \code{meancount} 
are both omitted, \code{meancount} is fixed in order to obtain roughly $(4n)^{2/5}$ cells, 
with $n$ the length of the data set \citep{Vose10}. Using this default option the two previous fits are 
compared as follows, 
giving the preference
to the negative binomial distribution, from both Chi-squared statistics and information criteria:
%%% R code
<<fittoxocara.poisnbinom.gof, echo=TRUE, fig=FALSE>>=
gofstat(list(ftoxo.P,ftoxo.nb),
        fitnames = c("Poisson","negative binomial"))
@
